### 2013-09-21 results.tex
P79 seg vol added

Figure~\ref{fig:mr_anatomy} shows the anatomic zones and some anatomic
orientation labels in the prostate of a representative study subject.  The
zonal anatomy of the prostate was manually segmented (Figure XX) across the
image stack, and 3D models of the zonal anatomy volumes were rendered (Figure
XX).

@@

INSERT MR IMAGE SEGMENTS HERE (P79)

INSERT 3D MODEL OF MR HERE

>>>>

Figure~\ref{fig:mr_anatomy} shows the anatomic zones and some anatomic
orientation labels in the prostate of a representative study subject.  The
zonal anatomy of the prostate was manually segmented
(Figure~\ref{fig:mr_segs_vol}, bottom left) across the image stack, and 3D
models of the zonal anatomy volumes were rendered
(Figure~\ref{fig:mr_segs_vol}, top).

@@

\input{fig_mr_segs_vol}
